Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Edits.

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek\ uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% Implemented in Psiphon's version.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
This second technique doesn't work on all services:
notably Google App Engine doesn't support streaming downloads of this kind.

@@

Domain fronting shares a weakness with decoy routing,
which is that the overt and covert destinations lie on different
network paths.
The difference in paths may create side channels---latency measurements for instance---that
enable the censor to
distinguish fronted traffic from traffic that is truly destined
to the front domain.
For example, a CDN can be expected to have responses
to some fraction of requests already in cache,
and respond to those requests with low latency.
Fronted traffic, on the other hand, always continues all the way
to the origin server after reaching the CDN (as if nothing were ever cached),
resulting in a higher latency.
Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
who compared empirical round-trip-time distributions using a
Kolmogorov--Smirnov test.
% time between ChangeCipherSpec and ApplicationData

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Concurrent users of \meek\ with Tor.}
\label{fig:clients}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{Daily unique users of \meek\ with Psiphon3 (note vertical axis).}
\label{fig:clients}
\end{figure}

>>>>

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek\ uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
This second technique doesn't work on all services:
notably Google App Engine doesn't support streaming downloads of this kind.

% Overhead estimate.
As discussed in Section~\ref{sec:trafficanalysis},
the same TLS session is used for many requests,
so the overhead of the TLS handshake is amortized.

@@

Domain fronting shares a potential weakness with decoy routing,
which is that the overt and covert destinations lie on different
network paths.
The difference in paths may create side channels---latency measurements for instance---that
enable the censor to
distinguish fronted traffic from traffic that is truly destined
to the front domain.
For example, a CDN can be expected to have responses
to some fraction of requests already in cache,
and respond to those requests with low latency.
Fronted traffic, on the other hand, always continues all the way
to the origin server after reaching the CDN (as if nothing were ever cached),
resulting in a higher latency.
Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
who compared empirical round-trip-time distributions using a
Kolmogorov--Smirnov test.
% time between ChangeCipherSpec and ApplicationData

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{
Concurrent users of \meek\ with Tor.
}
\label{fig:clients}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek\ with Psiphon (note vertical axis).
The decrease at the end of June
was caused by an unblocking event that made meek unnecessary for some users.
}
\label{fig:clients}
\end{figure}
